Model Samples Processing

### 2020-02-10 stats/model.Rmd
update model run

```{r}
library(tidyverse)
library(rwebppl)
library(brms)
library(coda)
library(ggthemes)
library(readxl)
library(ggpubr)
library(stringr)
library(matrixStats)
library(data.table)
library(bigmemory)
library(langcog)

@@

plot_model_pred_flat <- model_pred_flat%>%
  group_by(alignment, item, age)%>%
  summarise(mean = estimate_mode(pred),
            ci_lower = hdi_lower(pred),
            ci_upper = hdi_upper(pred))

data_comb %>%
  select(-age)%>%
  mutate(age = age_month,
         item = as.character(item))%>%
  left_join(model_pred_prag)%>%
  mutate(like = ifelse(correct == 1, pred, 1 - pred),
         log_like_prag = log(like))%>%
  select(chain, iteration, age, alignment,item,log_like_prag)%>%
  saveRDS(.,"../saves/log_like_prag")

log_like_global <- data_comb %>%
  select(-age)%>%
  mutate(age = age_month,
         item = as.character(item))%>%
  left_join(model_pred_global)%>%
  mutate(like = ifelse(correct == 1, pred, 1 - pred),
         log_like_global = log(like))%>%
  select(chain,iteration, age, alignment,item,log_like_global)

log_like_flat <- data_comb %>%
  select(-age)%>%
  mutate(age = age_month,
         item = as.character(item))%>%
  left_join(model_pred_flat)%>%
  mutate(like = ifelse(correct == 1, pred, 1 - pred),
         log_like_flat = log(like))%>%
  select(chain,iteration,age, alignment,item,log_like_flat)

model_comp <- log_like_prag%>%
  left_join(log_like_global)%>%
  left_join(log_like_flat)%>%
  mutate(prag_vs_global = log_like_prag - log_like_global,
         prag_vs_flat = log_like_prag - log_like_flat)%>%
  na.omit(prag_vs_global,prag_vs_flat)%>%
  summarize(prag_vs_global = logSumExp(prag_vs_global),
            prag_vs_flat = logSumExp(prag_vs_flat))

@@

>>>>

```{r}
library(tidyverse)
library(rwebppl)
#library(brms)
library(coda)
library(ggthemes)
library(readxl)
library(ggpubr)
library(stringr)
library(matrixStats)
library(data.table)
library(bigmemory)
#library(langcog)

@@

```{r}
log_like_prag <- data_comb %>%
  select(-age)%>%
  mutate(age = age_month,
         item = as.character(item))%>%
  left_join(readRDS("../saves/model_pred_prag.rds"))%>%
  mutate(like = ifelse(correct == 1, pred, 1 - pred),
         log_like = log(like),
         model = "prag",
         id = 1:length(log_like))%>%
  select(id, model,chain, iteration, age, alignment,item,log_like)

gc()

log_like_global <- data_comb %>%
  select(-age)%>%
  mutate(age = age_month,
         item = as.character(item))%>%
  left_join(readRDS("../saves/model_pred_global.rds"))%>%
  mutate(like = ifelse(correct == 1, pred, 1 - pred),
         log_like = log(like),
         model = "global",
         id = 1:length(log_like))%>%
  select(id, model,chain,iteration, age, alignment,item,log_like)

gc()

saveRDS(log_like_global, "../saves/log_like_global.rds")

comp <- bind_rows(
  readRDS("../saves/log_like_prag.rds")%>%mutate(id = 1:length(log_like)), 
  readRDS("../saves/log_like_global.rds")%>%mutate(id = 1:length(log_like))
)%>%
  spread(model, log_like)%>%
  mutate(prag_vs_global = prag - global)

log_like_flat <- data_comb %>%
  select(-age)%>%
  mutate(age = age_month,
         item = as.character(item))%>%
  left_join(readRDS("../saves/model_pred_flat.rds"))%>%
  mutate(like = ifelse(correct == 1, pred, 1 - pred),
         log_like_flat = log(like))%>%
  select(chain,iteration,age, alignment,item,log_like_flat)

gc()

log_like_prior <- data_comb %>%
  select(-age)%>%
  mutate(age = age_month,
         item = as.character(item))%>%
  left_join(readRDS("../saves/model_pred_prior.rds"))%>%
  mutate(like = ifelse(correct == 1, pred, 1 - pred),
         log_like_prior = log(like))%>%
  select(chain,iteration,age, alignment,item,log_like_prior)

gc()

prag_vs_global <- log_like_prag%>%
  left_join(log_like_global)%>%
  mutate(prag_vs_global = log_like_prag - log_like_global)%>%
  na.omit(prag_vs_global)%>%
  summarize(prag_vs_global = logSumExp(prag_vs_global))%>%
  saveRDS(.,"../saves/model_comp_prag_vs_global.rds")

@@

xx %>%
  spread(model, log_like)

comp <- comp%>%
  na.omit(prag_vs_global)

p_g_comp <- comp %>%
  summarize(prag_vs_global = logSumExp(prag_vs_global))

model_pred_prag

bind_rows(

  data_comb %>%
    mutate(age = age_month,
    item = as.character(item))%>%
    left_join(model_pred_prag)%>%
    mutate(like = ifelse(correct == 1, pred, 1 - pred),
         log_like = log(like),
         model = "prag",
         id = 1:length(log_like))%>%
  select(id, model,chain,iteration, age, alignment,item,log_like),

  data_comb %>%
    left_join(model_pred_prag)%>%
    mutate(like = ifelse(correct == 1, pred, 1 - pred),
         log_like = log(like),
         model = "global")
)%>%
  spread(model, log_like)%>%
  mutate(prag_vs_global = prag - global)

%>%
  summarise(logBF = logSumExp(prag_vs_global))

### 2020-02-10 stats/model_sample_processing.Rmd
update model run

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
```

@@

model <- bind_rows(
 fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain4.csv",header = T)%>%mutate(chain = 4),
 fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain5.csv",header = T)%>%mutate(chain = 5),
 fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain6.csv",header = T)%>%mutate(chain = 6)
)

@@

saveRDS(item_params, "../saves/item_params_2.rds")

>>>>

hdi_lower<- function(s){
  m <- HPDinterval(mcmc(s))
  return(m["var1","lower"])
}
```
```{r}

# remove chain 6

```{r}
readRDS("../saves/item_params.rds")%>%
  filter(chain != 6)%>%
  saveRDS(., "../saves/item_params.rds")

readRDS("../saves/global_params.rds")%>%
  filter(chain != 6)%>%
  saveRDS(., "../saves/global_params.rds")

readRDS("../saves/item_sigma.rds")%>%
  filter(chain != 6)%>%
  saveRDS(., "../saves/item_sigma.rds")

readRDS("../saves/model_pred_prag.rds")%>%
  filter(chain != 6)%>%
  saveRDS(., "../saves/model_pred_prag.rds")

readRDS("../saves/model_pred_global.rds")%>%
  filter(chain != 6)%>%
  saveRDS(., "../saves/model_pred_global.rds")

readRDS("../saves/model_pred_flat.rds")%>%
  filter(chain != 6)%>%
  saveRDS(., "../saves/model_pred_flat.rds")

readRDS("../saves/model_pred_prior.rds")%>%
  filter(chain != 6)%>%
  saveRDS(., "../saves/model_pred_prior.rds")

@@

model <- bind_rows(
 fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain4.csv",header = T)%>%mutate(chain = 1),
fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain4.csv",header = T)%>%mutate(chain = 2), 
fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain4.csv",header = T)%>%mutate(chain = 3),
 fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain5.csv",header = T)%>%mutate(chain = 4),
 fread("../webppl/output/samples-reFactor-noRandomEffects_mcmc-100000_burn50000_lag5_chain6.csv",header = T)%>%mutate(chain = 5)
)

@@

saveRDS(item_params, "../saves/item_params.rds")
